%-------------------------
% Resume in Latex
% Author : Karthik Hosur
% Based off of: https://github.com/karthikhosur/ 
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Karthik Hosur} \\ \vspace{1pt}
    \small +91 9611131081$|$ \href{mailto:x@x.com}{\underline{karthikhosur15@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/karthikhosur}} $|$
    \href{https://github.com/...}{\underline{github.com/karthikhosur}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Visvesvaraya Technological University}{Bangalore, India}
      {Bachelor of Engineering in Computer Science \& Engineering}{Aug. 2016 -- Aug 2020}
   % \resumeSubheading
      %{Blinn College}{Bryan, TX}
      %{Associate's in Liberal Arts}{Aug. 2014 -- May 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
     {Software Engineer- Full Stack \& AI}{July 2020 -- Present}
      {TalentMicro Innovations Pvt. Ltd.}{Bangalore, TX}
      \resumeItemListStart
        \resumeItem{Developed a Resume Parser and a Resume ranking tool using Natural Language Processing and Deep Learning}
    
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineering Intern}{Feb. 2018 -- June 2020}
      {HireCraft Software Pvt. Ltd.}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Worked on a Big Five factor personality detection mobile application to classify candidates based on personality for recruitment. }
        
    \resumeItemListEnd

    \resumeSubheading
      {Research Intern}{July 2019 -- Sep. 2019}
      {Incarnus Technologies India Pvt. Ltd.}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Designed and integrated chatbot to ArcusAir, a Hospital Management System to help the users like Doctors, Technicians, and Nurses to retrieve knowledge base using natural language input by voice or text.}
        
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Personality Evaluation using Sentiment Analysis} $|$ \emph{Python, Swift, Docker}}{}
          \resumeItemListStart
            \resumeItem{An iOS App to Classify the candidates text corpus based on different traits using Big Five Personality Evaluation}
            \resumeItem{The system replaces the traditional process of using a questionnaire to evaluate the candidates personality}
           \resumeItem{Application has been integrated into the HR system at HireCraft Software Pvt. Ltd.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Automatic Indian Number Plate Recognition System} $|$ \emph{Python, Flask, OpenCV, Angular}}{}
          \resumeItemListStart
            \resumeItem{Developed a CNN algorithm and trained it with Indian Number Plates to be recognized with a success rate of 86\%(The best publicly available model for Indian Number Plates)}
            \resumeItem{The application developed as an Angular Web App received appreciation from National Informatics Centre, Government of India}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PATENTS&PUBLICATION-----------
\section{Patents & Publications}
    \resumeSubHeadingListStart
          \resumeItemListStart
            \resumeItem{Patent filed on "A system and a method for exchanging information over chat system through structured forms(WO2018011653A1)"}
            \resumeItem{Patent filed on "A system and method for storing and securely sharing of information through an unique id(WO2016103109A1)"}
            \resumeItem{Research Paper on “Agriculture Crop Cost Prediction using Artificial Neural Networks“, International Journal of Advance Research, Ideas and Innovations in Technology, August 2018}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Awards-----------
\section{Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{CMR Leadership Award 2020}{, awarded to a distinguished graduating student for excellence in academics, behaviour and extracurricular activities} 
    }}
 \end{itemize}
 
 %-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C++, Swift, SQL, JavaScript, HTML/CSS, G} \\
     \textbf{Frameworks}{: React, Node.js, Flask, Angular, Django} \\
     \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
    }}
 \end{itemize}


%-------------------------------------------
%-----------Extracurricular Activities -----------
\section{Extracurricular Activities }
\small  \resumeItemListStart
            \resumeItem{Licensee and Lead Organizer at TEDxCMRIT }
            \resumeItem{Web developer of TEDxMarathahalli, 2018}
            \resumeItem{Organizer of “Hack-It-On” hackathon}
            \resumeItem{College representative for the Entrepreneurship Cell, IIT Bombay, 2017-18}
\resumeItemListEnd


%-------------------------------------------
\end{document}
